\cursedforest\ - A Random Forest Implementation for ``Big'' and ``Wide'' Data \\ Supplementary Information

### 2017-02-21 doc/publications/plos16/plos16.tex
removed margin note

\setlength{\marginparwidth}{5cm}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{placeins}
\usepackage{xspace} % see http:
%\usepackage{showframe}

@@

This may be because a large \mtry\ generates more correlated trees as the same important features have a higher chance
of being selected in all, not yielding good performance outcomes.  This issue is less pronounced for classification
tasks where random features can mimic the response variable, hence resulting more in a performance plateau.  
\marginpar{unclear what this means}
Increasing
the number of trees on the other hand improves performance especially when the trees are kept diverse (small \mtry) but
appropriate for large feature datasets (\mtry larger than default). \cursedforest's feature of parallelizing trees at
the node level hence caters perfectly to the requirement of large feature datasets as more trees can be built given a
fixed time budget.

>>>>

%\setlength{\marginparwidth}{5cm}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{placeins}
\usepackage{xspace} % see http:
%\usepackage{showframe}

@@

This may be because a large \mtry leads to more correlated trees as the same important features have a higher chance of
being selected in all, not yielding good performance outcomes.  This issue is less pronounced for classification error
where random features can mimic the response variable, hence resulting more in a performance plateau.  Increasing the
number of trees on the other hand improves performance especially when the trees are kept diverse (small \mtry) but
appropriate for large feature datasets (\mtry larger than default). \cursedforest's feature of parallelizing trees at
the node level hence caters perfectly to the requirement of large feature datasets as more trees can be built given a
fixed time budget.
